%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.2 (16/9/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% http://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\documentclass[]{Resume}
\usepackage{fancyhdr}
            
\pagestyle{fancy}
\fancyhf{}
 
\rfoot{Page \thepage \hspace{1pt}}
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{Steven Magdy}{ \urlstyle{same}
Al-Rehab City, Cairo | +201005265241 | \href{mailto:stevenmagdy92@gmail.com}{StevenMagdy92@gmail.com}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 

\subsection{B.S. in Computer Science}
\descript{Future University in Egypt}
\location{2016}
\sectionsep
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Languages \& Frameworks}
\location{Advanced:}
Java/Kotlin/Android \textbullet{} Swift/iOS
\location{Intermediate:}
Git \textbullet{} SQL \\
\location{Basic:}
Python \textbullet{} C++ \textbullet{} Objective-C
\sectionsep

\subsection{Libraries \& Tools}
\location{Java/Android:}
Retrofit \textbullet{} OkHttp \textbullet{} Gson \textbullet{} Moshi  \textbullet{} 
Dagger \textbullet{} Glide \textbullet{} RxJava \textbullet{} OneSignal \\
\vspace{\topsep}
\location{Swift/iOS:}
Firebase Cloud Messaging (FCM) \textbullet{} \\
Firebase Realtime Database \textbullet{} \\
Alamofire \textbullet{} SDWebImage \textbullet{} \\
CocoaPods \textbullet{} SwiftGen \textbullet{} SwiftLint \textbullet{}  \\
GRDB  \textbullet{} PureLayout
\sectionsep

\subsection{personal}
Teamwork \\
Presentation \\
Hard Worker \\
Quick Learner \\
Communication \\
Works well under pressure \\
Eager to Learn New Technologies
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Links} 
\href{http://github.com/stevenmagdy}{GitHub.com/\bf StevenMagdy} \\
 \href{http://www.linkedin.com/in/StevenMagdy}{LinkedIn.com/in/\bf StevenMagdy}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}
\runsubsection{Interface dmcc}
\descript{Android \& iOS Developer}
\location{Jan 2018 - Nov 2018 | Cairo, Egypt}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Worked as the project owner for a new project (Android, iOS and Backend) reporting to the CEO
\item Worked on a new iOS app as the sole developer (Unreleased).
\item Worked on a new iOS app for a governmental entity as the sole developer (Confidential).
\item Worked on integrating Unity modules into two existing iOS apps.
\item Worked on transitioning projects to use version control system (Git) \& streamline the collaboration process.
\item Worked on rewriting an Android app from scratch using Kotlin.
\item Worked on maintaining and modernizing 5 Android apps.
\end{tightemize}
\sectionsep

\runsubsection{CVS3/ASUGARDS}
\descript{Senior iOS \& Android Developer}
\location{Nov 2018 - Present | Cairo, Egypt}
%\begin{tightemize}
%\end{tightemize}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PERSONAL PROJECTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Personal projects}

\runsubsection{Cairo Metro}
\descript{Unreleased | \href{http://github.com/StevenMagdy/CairoMetro-iOS}{Source Code}}
iOS App for navigation between Metro stations.
\begin{tightemize}
\item \textbf{\href{http://github.com/realm/SwiftLint}{SwiftLint}} for Swift linting.
\item \textbf{\href{http://github.com/PureLayout/PureLayout}{PureLayout}} for designing UI programmatically.
\item \textbf{\href{http://github.com/groue/GRDB.swift}{GRDB}} for SQLite.
\item \textbf{\href{http://github.com/SwiftGen/SwiftGen}{SwiftGen}} for resources management.
\item \textbf{Google Analytics for Firebase} \& \textbf{\href{http://github.com/CocoaLumberjack/CocoaLumberjack}{CocoaLumberjack}} for analytics \& logging.
\item \textbf{Firebase Crashlytics} for crash reporting.
\end{tightemize}
\sectionsep

\runsubsection{carbon-now-sh for Xcode}
\descript{\href{http://itunes.apple.com/eg/app/id1451973144}{Mac App Store} | \href{http://github.com/StevenMagdy/CarboNow4Xcode}{Source Code}}
Xcode extension for opening up code selections in  \textbf{\href{http://carbon.now.sh/}{carbon.now.sh}}.
\begin{tightemize}
\item \textbf{\href{http://developer.apple.com/documentation/xcodekit}{XcodeKit}} for Xcode integration.
\item \textbf{\href{http://github.com/realm/SwiftLint}{SwiftLint}} for Swift linting.
\end{tightemize}
\sectionsep

\runsubsection{SMLocalize}
\descript{\href{http://cocoapods.org/pods/SMLocalize}{CocoaPod} | \href{http://github.com/StevenMagdy/SMLocalize}{Source Code}}
iOS Library for changing language at runtime.
\sectionsep

\runsubsection{Muzeillect}
\descript{\href{http://play.google.com/store/apps/details?id=com.steven.muzeillect}{Google Play} | \href{http://github.com/StevenMagdy/Muzeillect}{Source Code}}
Android extension for \textbf{\href{http://muzei.co}{Muzei}} for wallpapers from \textbf{\href{http://Archillect.com}{Archillect.com.}}
\begin{tightemize}
\item \textbf{\href{http://api.muzei.co}{Muzei API.}}
\item 100\% \textbf{\href{http://kotlinlang.org}{Kotlin.}}
\item \textbf{\href{http://github.com/JakeWharton/timber}{Timber}} for logging.
\item \textbf{\href{http://jsoup.org}{jsoup}} for HTML parsing.
\item \textbf{\href{http://square.github.io/okhttp}{OkHttp}} for networking.
\item \textbf{WorkManager}.
\item \textbf{Navigation Architecture Component} for Navigation.
\end{tightemize}
\sectionsep

\end{minipage} 
\end{document}  
\documentclass[]{article}
